\documentclass{exam}
\usepackage{amssymb}
\usepackage{lipsum} 
\usepackage[
backend=biber
]{biblatex}
\addbibresource{refs.bib}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,      
    urlcolor=blue,
    citecolor=blue,
}
\newcommand\labnr{11}
\newcommand\lab{Lab \labnr\ - File Input/Output}

\newcommand\uni{Technical University of Cluj-Napoca}
\newcommand\course{Computer Programming}

\newcommand\lvlez{$\bigstar$}
\newcommand\lvlmed{\lvlez\lvlez}
\newcommand\lvlhard{\lvlmed\lvlez}


\pagestyle{headandfoot}
\firstpageheader{}{}{}
\firstpagefootrule
\firstpageheadrule
\firstpagefooter{\sc\uni}{}{\sc\course, Lab \labnr}
\runningheader{\sc\uni}{}{\sc\course, Lab \labnr}
\runningheadrule
\runningfootrule
\runningfooter{}{\thepage}{}

\begin{document}
\begin{center}
   \vspace*{0cm}
   \bfseries\LARGE
   \lab
   \vspace*{1cm}
\end{center}

\begin{questions}
   \question  Create a text file containing a list of items a shop sells. An item is represented as a structure which
contains:
   \begin{itemize}
      \item a code
      \item a name
      \item a unit of measure
      \item the amount
      \item the price per unit
   \end{itemize} 
   The items are read from the keyboard. \lvlez
   \question Same as the previous problem, but use a binary file. \lvlmed
   \question Write a program to concatenate 2 text files. \lvlez
   \question Write a program to concatenate 2 binary files. \lvlez
   \question Write a program that prints the contents of a binary file to the screen in hexadecimal. Print a new line after every 64 bytes. \lvlez
   \question Write a program to find all the occurrences of a word in a text file. The program will print to the screen the line and the column where each occurrence of the word is found. \lvlmed
   \question Write a program which compares the contents of two existing text files and prints the lines which are different. \lvlez
   \question Starting with the file created at problem 1 or 2, create another one where the items are sorted ascending on their code field. \lvlmed
   \question Using the file created at problem 1 or 2, write functions to add, search and delete items from the shop. \lvlhard
   \question Using the files created at problem 1 or 2, write a function to merge 2 data files. If an item is found in both files the quantity of the item in the new file should be the sum of the quantities in the 2 original files. \lvlhard
\end{questions}
\medskip
\section*{References}
\begin{itemize}
   \item Pb. 1, 7-10 \cite{cplab11}
\end{itemize}
\printbibliography[heading=none]
\end{document}