\documentclass{exam}
\usepackage{amssymb}
\usepackage{lipsum} 
\usepackage[
backend=biber
]{biblatex}
\addbibresource{refs.bib}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,      
    urlcolor=blue,
    citecolor=blue,
}
\newcommand\labnr{6}
\newcommand\lab{Lab \labnr\ - Modular Programming}

\newcommand\uni{Technical University of Cluj-Napoca}
\newcommand\course{Computer Programming}

\newcommand\lvlez{$\bigstar$}
\newcommand\lvlmed{\lvlez\lvlez}
\newcommand\lvlhard{\lvlmed\lvlez}


\pagestyle{headandfoot}
\firstpageheader{}{}{}
\firstpagefootrule
\firstpageheadrule
\firstpagefooter{\sc\uni}{}{\sc\course, Lab \labnr}
\runningheader{\sc\uni}{}{\sc\course, Lab \labnr}
\runningheadrule
\runningfootrule
\runningfooter{}{\thepage}{}

\begin{document}
\begin{center}
   \vspace*{0cm}
   \bfseries\LARGE
   \lab
   \vspace*{1cm}
\end{center}

\begin{questions}   
   \question Create a module that defines the following operations on arrays of integers: minimum, maximum, average, median. \lvlez
   \question Create a module that implements sets and the operations on sets (union, intersection, difference). \lvlmed
   \question Create a module that implements the K nearest neighbors algorithm. 
   Given:
   \begin{itemize}
      \item $S$: a set of $n$ 2d points identified by their x and y coordinates and a letter $l$ (label). 
      \item $p$: another 2d point that has no label
      \item $k$: a positive integer
   \end{itemize}

   Find the closest $k$ points from $S$ to $p$ and return the label most commonly found among them. 
   
   Example: \begin{itemize}
      \item $p$ = (x=1, y=1)
      \item $k$ = 3 
      \item $S$ = \{(x=0, y=0, l='r'), (x=0, y=1, l='r'), (x=-1.5, y=1.5, l='r'), (x=1.2, y=1.2, l='b'), (x=2, y=1, l='b')\}
   \end{itemize}
      The closest $k=3$ points from $S$ to $p$ are \{(x=0, y=1, l='r'), (x=1.2, y=1.2, l='b'), (x=2, y=1, l='b')\}. In these 3 points the label 'b' appears 2 times and the label 'r' appears 1 time, so the result is 'b' (the label with the most apparitions).
   
   Hint: In order to compute the distance between 2 points use the Euclidean distance: \[d(a,b)=\sqrt[]{(a_x-b_x)^2+(a_y-b_y)^2}\]

   Hint: In order to store the points you can use either an array of structs or a matrix of $n \times 3$ floats, where \verb|m[i][0]| is the x coordinate of the i'th point, \verb|m[i][1]| is the y coordinate of the i'th point, etc. \lvlhard{}
\end{questions}
\medskip
\section*{References}
\begin{itemize}
   \item Pb. 2 \cite{cplab06}
\end{itemize}
\printbibliography[heading=none]
\end{document}